Proof nets for first-order additive linear logic

### 2018-03-23 Archive/ALL1-backup-5.tex
some cleanup

\newcommand\qrr[1]{
  \ifx#1+\expandafter\@qrr\else
  \ifx#1*\*\mathrm R\else
  \ifx#1!\forall\mathrm R\else
  \ifx#1?\expandafter\@@qrr\else
  \ifx#11\mathrm{ax}\else
  #1\mathrm R
  \fi\fi\fi\fi\fi
}
\newcommand\@qrr[1]{+\mathrm R,#1}
\newcommand\@@qrr[1]{\exists\mathrm R,#1}
\newcommand\srr[1]{
  \ifx#1+\expandafter\@srr\else
  \ifx#1*\*\mathrm S\else
  \ifx#1!\forall\mathrm S\else
  \ifx#1?\exists\mathrm S\else 
  \ifx#11\mathrm{axS}\else
  #1\mathrm S  \fi\fi\fi\fi\fi
}
\newcommand\@srr[1]{+_{#1}\mathrm S}
\newcommand\urr[1]{
  \ifx#1+\expandafter\@urr\else
  \ifx#1*\*\mathrm U\else
  \ifx#1!\forall\mathrm U\else
  \ifx#1?\exists\mathrm U\else 
  \ifx#11\mathrm{axU}\else
  #1\mathrm U
  \fi\fi\fi\fi\fi
}
\newcommand\@urr[1]{+_{#1}\mathrm U}

@@

\[
	\sigma = [a/y, s/x]
	\qquad
	\tau = [a/y, t/x]
\]
\[
	\upsilon = \rho[a/y, u/x]
	\qquad
	\rho = \mgu(s,t)
	\qquad
	 u=s\rho=t\rho
\]

@@

\begin{figure}
\noindent\hrule
\[
	\infer[\!\!\scriptstyle{\qrr1}]{\seq P{\dual P}}{}
\quad
	\infer[\!\!\scriptstyle{\qrr+i}]{\seq A{B_0\+B_1}}{\seq A{B_i}}
\quad
	\infer[\!\!\scriptstyle{\qrr*}]{\seq A{B\*C}}{\seq AB & \seq AC}
\quad
	\infer[\!\!\scriptstyle{\qrr?t}]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
\quad
	\infer[\!\!\scriptstyle{\qrr!~(a\,\notin\,\textsc{fv}(A))}]{\seq A{\forall a.B}}{\seq AB}
\]
\caption{A sequent calculus for $\all1$}
\label{fig:sequent calculus}
\end{figure}
%
%\begin{figure}
%\[
%\raisebox{.5ex}{$\qrr1$}\quad
%	\infer{\seq P{\dual P}}{}
%\quad\raisebox{.5ex}{$\qrr+i$}\quad
%	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
%\quad\raisebox{.5ex}{$\qrr*$}\quad
%	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
%\quad\raisebox{.5ex}{$\qrr?$}\quad
%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
%\quad\raisebox{.5ex}{$\qrr!$}\quad
%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
%\]
%\caption{A sequent calculus for $\all1$}
%\label{fig:sequent calculus}
%\end{figure}

@@

A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a partial function. The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[t/x]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else. We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.

A \defn{link} $(C,D)$ or $\link CD$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$, possibly carrying a witness map $\sigma$. We explicitly call a link $(C,D)$ without witness map \defn{clean}; otherwise $\sigma$ is assumed present. We assume the existential variables occurring in the range of $\sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$. A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it. The clean linking $\floor\lambda$ forgets the witness maps of a linking $\lambda$.

@@

An \defn{axiom link} is a link $\link PQ$ on two propositional atoms such that $P\sigma=\dual Q\sigma$. A linking consisting of axiom links is an \defn{axiom linking}. For a \emph{clean} axiom link $(P,Q)$ we require that a witness map $\sigma$ exists so that $P\sigma=\dual Q\sigma$.

%A link $\link[\varnothing]CD$ with empty witness map is \defn{clean}; it may then be rendered simply $(C,D)$. A linking or pre-net is \defn{clean} if all its links are. 
%We write $\floor\lambda$ respectively $\floor{\net\lambda AB}$ for the clean version of a linking or pre-net, which forgets the witness map for each link.

\begin{definition}
The \defn{de-sequentialization} $[\Pi]$ of a sequent proof $\prf\Pi AB$ is the pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
%
\begin{align*}
	\Deseq{\infer{\seq P{\dual P}}{}}QR &\quad=\quad \{\link QR\}
\\ \\
	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
	  {A'}{B_0'\+B'_1} 
	& \quad=\quad 
	\Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
\\ \\
	\Deseq{\infer{\seq A{B\*C}}{
	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
	  && 
	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
	& \quad=\quad 
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
	  \cup
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
\\ \\
	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
	  {A'}{\exists x.B'}
	& \quad=\quad 
	 \Deseq[{\sigma[t/x]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
	  {A'}{B'}
\\ \\
	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
	& \quad=\quad 
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
\end{align*}
%
The \defn{clean} de-sequentialization $\floor\Pi$ is $\net{\floor{\deseq[\varnothing]\Pi AB}}AB$:  as $[\Pi]$ but forgetting witness maps.
%
%of $\prf\Pi AB$ is the de-sequentialization $[\Pi]$ which forgets witness maps.
\end{definition}

Observe that the linking of $[\Pi]$ is an axiom linking, and that of $\floor\Pi$ a clean axiom linking.

@@

We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map. It is applied to a sequent proof, $\Pi\sigma$, by applying it to each formula in the proof $\Pi$. The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$. The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$.
%, and $\sigma|X$ is as $\sigma$ on the set of variables $X$ and undefined otherwise. 
We abbreviate the statement that a (universal) variable $a$ occurs free in some term in the range of $\sigma$, $a\in\fv(\sigma(x))$ for some $x$, by $a\in \sigma$. We define the following further operations on witness maps.

@@

To a clean axiom link $(P,Q)$ we assign an \defn{initial witness map} $\sigma(P,Q)$ as the least witness map $\sigma$ in $(\gen)$ such that $P\sigma=\dual Q\sigma$. In other words, $\sigma(P,Q)$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$. The \defn{initial witness assignment} $\lambda_\star$ to a clean axiom linking is:
\[
	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}~.
\]

@@

\subsection{Correctness and sequentialization}

Correctness and sequentialization for \all1 proof nets will be through \defn{coalescence}. This is a simple graph rewriting relation that gives top-down sequentialization, from the axioms to the conclusion of a proof. It is the additive counterpart to Danos \defn{contractibility} for multiplicative linear logic.

We will define two coalescence relations, one \defn{strict} $(\scoal)$ and one \defn{unifying} $(\ucoal)$. In the former, to join two slices the witness assignment must be the same; in the latter, witness assignments must be compatible, so that a common, more general witness map exists.

For sequentialization, the links in a pre-net are labelled with a sequent calculus axiom, and each coalescence rewrite step introduces one proof rule. To this end, let a \defn{labelled link} $\link AB^\Pi$ be a link carrying a sequent proof $\prf\Pi{A\sigma}{B\sigma}$, and a \defn{labelled linking} or \defn{labelled pre-net} one where every link is labelled. The \defn{initial labelling} $\lambda^\star$ of an axiom linking $\lambda$ is:
\[
	\lambda^\star = \{~\link PQ^\Pi~\mid~\link PQ\in\lambda~,~\Pi=~\infer{\seq{P\sigma}{Q\sigma}}{}~\}~.
\]
For correctness we may coalesce a pre-net without constructing a proof.

\begin{definition}
 \defn{Strict sequentialization} ($\scoal$) is the rewrite relation on labelled pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent. \defn{Strict coalescence} is the same relation ignoring proof labels, on pre-nets.
%
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{equation}
  	\net{\{\link A{B_i}^\Pi\}}A{B_0\+B_1} 
 ~\scoal~
	\net{\{\link A{B_0\+B_1} ^\Psi\}}A{B_0\+B_1}
\tag{$\srr+i$}
\end{equation}

\hfill $\text{where}\quad \Psi=~
  \vc{
   \infer  {\seq{A\sigma}{B_0\sigma\,\+\,B_1\sigma}}  {
  	\deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B_i\sigma}}  \Pi
  }}
$ \hspace*{20pt}

\begin{equation}
	\net{\{\link AB^\Pi,\link AC^\Phi\}}A{B\*C}
 ~\scoal~ 
	\net{\{\link A{B\*C}^\Psi\}}A{B\*C}
\tag{$\srr*$}
\end{equation}

\hfill $\text{where}\quad \Psi=~
  \vc{
   \infer  {\seq{A\sigma}{B\sigma\,\*\,C\sigma}}  {
    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi
    &
    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{C\sigma}}  \Phi    
  }}$ \hspace*{20pt}

\begin{equation}
	\net{\{\link AB^\Pi\}}A{\exists x.B}
 ~\scoal~ 
	\net{\{\link[\sigma\!\minus\!x]A{\exists x.B}^\Psi\}}A{\exists x.B}
\tag{$\srr?$}
\end{equation}

\hfill $\text{if}\quad\sigma(x)\,\neq\,\bot~,
		\quad
		\text{where}\quad \tau=\sigma\minus x
		\quad
		\text{and}\quad \Psi=~
  \vc{
   \infer  {\seq{A\tau}{\exists x.B\tau}}  {
    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi  
  }}
$ \hspace*{20pt}

\begin{equation}
	\net{\{\link AB\}}A{\forall a.B}
 ~\scoal~
	\net{\link A{\forall a.B}}A{\forall a.B}
\tag{$\srr!$}
\end{equation}

\hfill $\text{if}\quad a\notin\sigma~,
		\quad
		\text{where}\quad \Psi=~
  \vc{
   \infer  {\seq{A\sigma}{\forall a.B\sigma}}  {
    \deduce  [\rule{0pt}{1pt}]  {\seq{A\sigma}{B\sigma}}  \Pi  
  }}
$ \hspace*{20pt}

\medskip

\noindent
A pre-net $\net\lambda AB$ \defn{strict-coalesces} if it reduces in $(\scoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
\end{definition}

To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net\lambda AB\scoal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\scoal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, $\kappa'\subseteq\lambda'$, and $\lambda-\kappa=\lambda'-\kappa'$.

\begin{definition}
\defn{Unifying coalescence} ($\ucoal$) is the rewrite relation generated by the rules:
\[
	(\urr+i)~,~(\urr?)~,~(\urr!)
	\quad
	\text{are respectively as}
	\quad
	(\srr+i)~,~(\srr?)~,~(\srr!)
\]
except that ($\urr?$) does not require that $\sigma(x)$ is defined, plus the rule
\begin{equation}
	\net{\{\link AB^\Pi,\link[\tau]AC^\Phi\}}A{B\*C}
 ~\ucoal~ 
	\net{\{\link[\sigma\join\tau]A{B\*C}^\Psi\}}A{B\*C}
\tag{$\urr*$}
\end{equation}

\hfill $\text{if}\quad\sigma\coh\tau~,
		\quad
		\text{where}\quad \sigma\join\tau=\sigma\rho=\tau\rho
		\quad
		\text{and}\quad \Psi=~
  \vc{
   \infer  {\seq{A\sigma\rho}{B\sigma\rho\,\*\,C\sigma\rho}}  {
    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\sigma}{B\sigma}}  \Pi} \right)\rho
    &
    \left( \vc{\deduce  [\rule{0pt}{2pt}]  {\seq{A\tau}{C\tau}}  \Phi} \right)\rho   
  }}~.
$ \hspace*{20pt}

\medskip

\noindent
A pre-net $\net\lambda AB$ \defn{unifying-coalesces} if it reduces in $(\ucoal)$ to a single link $\net{\{\link[\varnothing]AB\}}AB$.
\end{definition}

%A pre-net $\net\lambda AB$ \defn{strict-} or \defn{unifying-coalesces} if it reduces in $(\scoal)$ respectively $(\ucoal)$ to a single link $\net{\link[\varnothing]AB}AB$. Here, we ignore the labelling with proofs, which means in particular that we need not instate a labelling to initiate coalescence.

%A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation , if it coalesces to a single clean link $\net{(A,B)^\Pi}AB$. In that case, it \defn{sequentializes} It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.

\begin{definition}
An \all1 \defn{witnessing proof net} or \defn{witness net} is a pre-net $\net\lambda AB$ with axiom linking $\lambda$ that strict-coalesces. It \defn{sequentializes} to a proof $\Pi$ if its initial labelling $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link[\varnothing]AB^\Pi\}}AB$.
\end{definition}

\begin{definition}
An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with clean axiom linking $\lambda$ such that its initial witness assignment $\net{\lambda_\star}AB$ unifying-coalesces. It \defn{sequentializes} to $\Pi$ if the initial labelling $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link[\varnothing]AB^\Pi\}}AB$.
\end{definition}

\begin{theorem}
For any \all1 proof $\Pi$:
\begin{enumerate}
\item the de-sequentialization $[\Pi]$ is a witness net that sequentializes to $\Pi$. 
\item the clean de-sequentialization $\floor\Pi$ is a unification net that sequentializes to a proof $\Phi$ such that $\Pi=\Phi\rho$ for some witness map $\rho$ (where universal variables may be captured).
\end{enumerate}
\end{theorem}

\begin{proof}
By induction on $\prf\Pi AB$, if $\lambda=[\Pi]_{A',B'}^\sigma$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star}AB$ reduces in $(\scoal)$ to $\net{\{\link{A'}{B'}^\Pi\}}AB$. Statement 1.\ is the specific case $\sigma=\varnothing$.
%
% Technical note: need to assume $\sigma$ contains no universally quantified variables in $A$ or $B$. 
%
For the second statement, by induction

 on $\prf\Pi AB$, if $\lambda=\floor{\deseq\Pi{A'}{B'}}$ where $A'\sigma=A$ and $B'\sigma=B$, then $\net{\lambda^\star_\star}AB$ reduces in $(\ucoal)$ to $\net{\{\link{A'}{B'}\}}{}{}$
\end{proof}

For two axiom linkings $\lambda$ and $\kappa$,

\begin{lemma}
If $\net\lambda AB$ with axiom linking $\lambda$ unifying-coalesces to $\net{\{\link{A'}{B'}\}}AB$ then $\net{\floor\lambda_\star}AB$ unifying-coalesces to $\net{\{\link[\rho]{A'}{B'}\}}AB$ with $\rho\gen\sigma$.
\end{lemma}

@@

%\end{document}

@@

\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{align}
	\net{\{\link AB,\link[\tau]AC\}}A{B\*C}
& ~\scoal~ 
	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\coh\tau
\tag{$\*$}
\end{align}

>>>>

\newcommand\qrr[1]{
  \ifx#1+\expandafter\@qrr\else
  \ifx#1*\*\mathrm R\else
  \ifx#1!\forall\mathrm R\else
  \ifx#1?\exists\mathrm R\else 
  \ifx#11\mathrm{ax}\else
  #1\mathrm R
  \fi\fi\fi\fi\fi
}
\newcommand\@qrr[1]{+_{#1}\mathrm R}
\newcommand\srr[1]{
  \ifx#1+\expandafter\@srr\else
  \ifx#1*\*\mathrm S\else
  \ifx#1!\forall\mathrm S\else
  \ifx#1?\exists\mathrm S\else 
  \ifx#11\mathrm{axS}\else
  #1\mathrm S  \fi\fi\fi\fi\fi
}
\newcommand\@srr[1]{+_{#1}\mathrm S}
\newcommand\urr[1]{
  \ifx#1+\expandafter\@urr\else
  \ifx#1*\*\mathrm U\else
  \ifx#1!\forall\mathrm U\else
  \ifx#1?\exists\mathrm U\else 
  \ifx#11\mathrm{axU}\else
  #1\mathrm U
  \fi\fi\fi\fi\fi
}
\newcommand\@urr[1]{+_{#1}\mathrm U}

@@

\[
	\sigma = [y\mapsto a, x\mapsto s]
	\qquad
	\tau = [y\mapsto a, x\mapsto t]
\]
\[
	\upsilon = \rho[y\mapsto a, x\mapsto u]
	\qquad
	\rho = \mgu(s,t)
	\qquad
	 u=s\rho=t\rho
\]

@@

\begin{figure}
\noindent\hrule
\[
	\infer[\!\!\scriptstyle{\qrr1}]{\seq P{\dual P}}{}
\quad
	\infer[\!\!\scriptstyle{\qrr+i}]{\seq A{B_0\+B_1}}{\seq A{B_i}}
\quad
	\infer[\!\!\scriptstyle{\qrr*}]{\seq A{B\*C}}{\seq AB && \seq AC}
\quad
	\infer[\!\!\scriptstyle{\qrr?}]{\seq A{\exists x.B}}{\seq A{B[t/x]}}
\quad
	\infer[\!\!\scriptstyle{\qrr!~(a\,\notin\,\textsc{fv}(A))}]{\seq A{\forall a.B}}{\seq AB}
\]
\caption{A sequent calculus for $\all1$}
\label{fig:sequent calculus}
\end{figure}
%
%\begin{figure}
%\[
%\raisebox{.5ex}{$\qrr1$}\quad
%	\infer{\seq P{\dual P}}{}
%\quad\raisebox{.5ex}{$\qrr+i$}\quad
%	\infer{\seq A{B_0\+B_1}}{\seq A{B_i}}
%\quad\raisebox{.5ex}{$\qrr*$}\quad
%	\infer{\seq A{B\*C}}{\seq AB && \seq AC}
%\quad\raisebox{.5ex}{$\qrr?$}\quad
%	\infer{\seq A{\exists x.B}}{\seq A{B[t/x]}}
%\quad\raisebox{.5ex}{$\qrr!$}\quad
%	\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]{\seq A{\forall a.B}}{\seq AB}
%\]
%\caption{A sequent calculus for $\all1$}
%\label{fig:sequent calculus}
%\end{figure}

@@

A \defn{witness map} $\sigma\colon \varE \rightharpoonup \terms$ is a substitution map which assigns terms to existential variables, given as a partial function. The \defn{empty} witness map $\varnothing$ is the everywhere undefined partial function, and the map $\sigma[x\mapsto t]$ substitutes $t$ for $x$ and is as $\sigma$ everywhere else. We express by $\sigma(x)=\bot$ that $\sigma$ is undefined for $x$.

A \defn{link} $\link CD$ on a sequent $\seq AB$ is a pair of subformulas $C\leq A$ and $D\leq B$ along with a witness map $\sigma$. We assume the existential variables occurring in the range of $\sigma$ to be fresh, i.e.\ distinct from any existentially quantified variable in $\seq AB$. A \defn{linking} $\lambda$ on the sequent $\seq AB$ is a set of links on it.% $\seq AB$.

@@

An \defn{axiom} link is a link $\link PQ$ on two propositional atoms. A linking consisting of axiom links is an \defn{axiom linking}. A link $\link[\varnothing]CD$ with empty witness map is \defn{clean}; it may then be rendered simply $(C,D)$. A linking or pre-net is \defn{clean} if all its links are.

@@

We will write $A\sigma$ for the application of the witness map $\sigma\colon\varE\rightharpoonup\terms$ to the formula $A$ as a substitution map. The \defn{composition} of two maps is written $\sigma\tau$, where $A(\sigma\tau)=(A\sigma)\tau$. The map $\sigma\minus x$ is undefined on $x$ and otherwise as $\sigma$.
%, and $\sigma|X$ is as $\sigma$ on the set of variables $X$ and undefined otherwise. 
We abbreviate the statement that a (universal) variable $a$ occurs free in some term in the range of $\sigma$, $a\in\fv(\sigma(x))$ for some $x$, by $a\in \sigma$. We define the following further operations on witness maps.

@@

@@

\subsection{Coalescence}

We will define two \defn{coalescence} relations, one \defn{strict} $(\scoal)$ and one \defn{unifying} $(\ucoal)$.

\begin{definition}
\defn{Strict coalescence} ($\scoal$) is the rewrite relation on pre-nets generated by the following rules, which apply symmetrically to the first formula in the sequent.
%
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{align}
  	\net{\{\link AB\}}A{B\+C} 
& ~\scoal~
	\net{\{\link A{B\+C}\}}A{B\+C}
\tag{$\srr+1$}
\\[5pt]
        \net{\{\link AC\}}A{B\+C}
& ~\scoal~  
	\net{\{\link A{B\+C}\}}A{B\+C}
\tag{$\srr+2$}
\\[5pt]
	\net{\{\link AB,\link AC\}}A{B\*C}
& ~\scoal~ 
	\net{\{\link A{B\*C}\}}A{B\*C}
\tag{$\srr*$}
\\[5pt]	
	\net{\{\link AB\}}A{\exists x.B}
& ~\scoal~ 
	\net{\{\link[\sigma\!\minus\!x]A{\exists x.B}\}}A{\exists x.B} \quad \text{if }\sigma(x)\,\neq\,\bot
\tag{$\srr?$}
\\[5pt]
	\net{\{\link AB\}}A{\forall a.B}
& ~\scoal~ 
	\net{\link A{\forall a.B}}A{\forall a.B} \quad \text{if }a\notin\sigma
\tag{$\srr!$}
\end{align}
%
\defn{Unifying coalescence} ($\ucoal$) is the rewrite relation generated by the following rules:
\[
	(\urr+i)~,~(\urr?)~,~(\urr!)
	\quad
	\text{are respectively as}
	\quad
	(\srr+i)~,~(\srr?)~,~(\srr!)
\]
except $\urr?$ does not require that $\sigma(x)$ is defined, plus the rule
\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{align}
	\net{\{\link AB,\link[\tau]AC\}}A{B\*C}
& ~\ucoal~ 
	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\coh\tau~.
\tag{$\urr*$}
\end{align}
%
A pre-net $\net\lambda AB$ \defn{coalesces}, in either relation $(\scoal)$ or $(\ucoal)$, if it coalesces to a single clean link $\net{(A,B)}AB$. It \defn{strongly coalesces} if every coalescence sequence can be extended to reach $\net{(A,B)}AB$.
\end{definition}

To be explicit, to generate coalescence as a rewrite relation means the following: a pre-net coalesces to another, $\net\lambda AB\scoal \net{\lambda'}AB$ if and only if there is a rewrite rule $\net\kappa CD\scoal\net{\kappa'} CD$ such that $C\leq A$, $D\leq B$, $\kappa\subseteq\lambda$, $\kappa'\subseteq\lambda'$, and $\lambda-\kappa=\lambda'-\kappa'$; and likewise for $(\ucoal)$.

\begin{definition}
An \all1 \defn{witnessing proof net} or \defn{witness net} is a pre-net $\net\lambda AB$ with $\lambda$ an axiom linking, that strict-coalesces.
\end{definition}

Coalescence on a clean axiom linking is initiated by assigning each link $(P,Q)$ an \defn{initial witness map} $\sigma(P,Q)$ which, if it exists, is the most general witness map $\sigma$ such that $P\sigma=\dual Q\sigma$. In other words, $\sigma(P,Q)$ is the most general unifier ($\textsc{mgu}$) of $P$ and $\dual Q$. If it exists, we call the link $(P,Q)$ \defn{coherent}; a linking is \defn{coherent} if all its links are. For a coherent axiom linking $\lambda$ we define the \defn{initial witness assignment} $\lambda_\star$ to be:
\[
	\lambda_\star = \{~\link PQ~\mid~(P,Q)\in\lambda~,~\sigma=\sigma(P,Q)~\}~.
\]

\begin{definition}
An \all1 \defn{unification proof net} or \defn{unification net} is a pre-net $\net\lambda AB$ with a clean, coherent axiom linking $\lambda$, such that $\net{\lambda_\star}AB$ unifying-coalesces.
\end{definition}

\subsection{(De-)Sequentialization}

 We write $\floor\lambda$ respectively $\floor{\net\lambda AB}$ for the clean version of a linking or pre-net, which forgets the witness map for each link.
%

\begin{definition}
The \defn{de-sequentialization} $[\Pi]$ of a sequent proof $\prf\Pi AB$ is the pre-net $\net{\deseq[\varnothing]\Pi AB} AB$ where $\deseq-AB$ is defined as follows.
%
\[
\begin{array}{ccl}
	\Deseq{\infer{\seq P{\dual P}}{}}QR &=& \{\link QR\}
\\ \\
	\Deseq{\infer {\seq A {B_0\+B_1}} {\deduce [\rule{0pt}{1pt}] {\seq A{B_i}} \Pi }}
	  {A'}{B_0'\+B'_1} 
	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq A{B_i}}\Pi}{A'}{B_i'}
\\ \\
	\Deseq{\infer{\seq A{B\*C}}{
	  \deduce[\rule{0pt}{1pt}]{\seq AB}\Pi 
	  && 
	  \deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}}{A'}{B'\*C'}
	&=& \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
	  \cup
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AC}\Sigma}{A'}{C'}
\\ \\
	\Deseq{\infer{\seq A{\exists x.B}}{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}}
	  {A'}{\exists x.B'}
	&=&
	 \Deseq[{\sigma[x\mapsto t]}]{\deduce[\rule{0pt}{1pt}]{\seq A{B[t/x]}}\Pi}
	  {A'}{B'}
\\ \\
	\Deseq{\infer[\!\!\scriptstyle{a\,\notin\,\textsc{fv}(A)}]
	  {\seq A{\forall a.B}}{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}}{A'}{\forall a.B'}
	&=&
	  \Deseq{\deduce[\rule{0pt}{1pt}]{\seq AB}\Pi}{A'}{B'}
\end{array}
\]
The \defn{clean} de-sequentialization $\floor\Pi$ of $\prf\Pi AB$ is $\floor{[\Pi]}$.
\end{definition}

Observe that the pre-net $[\Pi]$ has a strict axiom linking and $\floor\Pi$ a clean axiom linking.

@@

@@

\renewcommand{\+}{{+}}
\renewcommand{\*}{{\times}}
\begin{align}
	\net{\{\link AB,\link[\tau]AC\}}A{B\*C}
& ~\coal~ 
	\net{\{\link[\sigma\join\tau]A{B\*C}\}}A{B\*C}\quad\text{if }\sigma\comp\tau
\tag{$\*$}
\end{align}
